\documentclass[
	%parspace, % Add vertical space between paragraphs
	%noindent, % No indentation of first lines in each paragraph
	%nohyp, % No hyphenation of words
	%twoside, % Double sided format
	%draft, % Quicker draft compilation without rendering images
	%final, % Set final to hide todos
]{elteikthesis}[2023/04/10]

% The minted package is also supported for source highlighting
% See elteikthesis_minted.tex for example
%\usepackage[newfloat]{minted}
\usepackage{wrapfig}
\usepackage[inkscapeformat=png]{svg}
\usepackage{biblatex}

\lstdefinelanguage{Dockerfile}
{
  morekeywords={FROM, RUN, CMD, LABEL, MAINTAINER, EXPOSE, ENV, ADD, COPY,
    ENTRYPOINT, VOLUME, USER, WORKDIR, ARG, ONBUILD, STOPSIGNAL, HEALTHCHECK,
    SHELL},
  morecomment=[l]{\#},
  morestring=[b]"
}

% Document's metadata
\title{Automated testing of applications with graphical user interface in cloud-native environments} % title
\date{2023} % year of defense

% Author's metadata
\author{Molnár Líviusz}
\degree{Computer Science BSc}

% Superivsor(s)' metadata
\supervisor{Horváth Győző} % internal supervisor's name
\affiliation{Associate Professor} % internal supervisor's affiliation
%\extsupervisor{Jane Doe} % external supervisor's name
%\extaffiliation{Senior Developer} % external supervisor's affiliation

% University's metadata
\university{Eötvös Loránd University} % university's name
\faculty{Faculty of Informatics} % faculty's name
\department{Dept. of Media & Educational Technology} % department's name
\city{Budapest} % city
\logo{elte_cimer_szines} % logo

% Add bibliography file
\addbibresource{elteikthesis.bib}

% The document
\begin{document}

% Set document language
%\documentlang{hungarian}
\documentlang{english}

% List of todos (not in the final document)
%\listoftodos[\todolabel]

% Title page (mandatory)
\maketitle
% Topic declaration page (mandatory) - can also be attached instead
%\includepdf{topicdeclaration.pdf}

% Table of contents (mandatory)
\tableofcontents
\cleardoublepage

% Main content
\input{samples_en/intro.tex}
\cleardoublepage

\input{samples_en/user.tex}
\cleardoublepage

\input{samples_en/impl.tex}
\cleardoublepage

\input{samples_en/sum.tex}
\cleardoublepage

% Acknowledgements (optional) - in case your thesis received funding or would like to express special thanks to someone
\chapter*{\acklabel}
\addcontentsline{toc}{chapter}{\acklabel}
I would like to recognize Zvara Zoltán for his significant contribution to the creation of the SeleniumTest operator. His knowledge and commitment were crucial in making this endeavor a success. I am incredibly appreciative of his advice and assistance during the development process. Zvara, I appreciate your sharing your knowledge with me and your support.
\cleardoublepage
% Bibliography (mandatory)
\phantomsection
\addcontentsline{toc}{chapter}{\biblabel}
\chapter{Bibliography}
\label{Bibliography}
References
\begin{itemize}
    \item “Go | Operator SDK.” Operator SDK, https://sdk.operatorframework.io/docs/building-operators/golang/. Accessed 5 May 2023.
    \item “Kubernetes.” Kubernetes, https://kubernetes.io/. Accessed 5 May 2023.
    \item “Minikube Start | Minikube.” Minikube, https://minikube.sigs.k8s.io/docs/start/. Accessed 5 May 2023.
    \item prometheus-operator. “GitHub - Prometheus-Operator/Kube-Prometheus: Use Prometheus to Monitor Kubernetes and Applications Running on Kubernetes.” GitHub, https://github.com/prometheus-operator/kube-prometheus. Accessed 5 May 2023.
    \item “Selenium.” Selenium, https://www.selenium.dev/. Accessed 5 May 2023.
    \item Software, Aerokube. “Moon - A Cross Browser Selenium, Cypress, Playwright and Puppeteer Solution for Kubernetes or Openshift Cluster.” Aerokube | Efficient Browser Automation Infrastructure, https://aerokube.com/moon/latest/. Accessed 5 May 2023.
\end{itemize}
\printbibliography[title=\biblabel]
\cleardoublepage

% List of figures (optional) - useful over 3-5 figures
\phantomsection
\addcontentsline{toc}{chapter}{\lstfigurelabel}
\listoffigures
\cleardoublepage

% List of codes (optional) - useful over 3-5 code samples
\phantomsection
\addcontentsline{toc}{chapter}{\lstcodelabel}
\lstlistoflistings
\cleardoublepage

% List of symbols (optional)
%\printnomenclature

\end{document}
